### 2016-03-17 doc/thesis/methods.tex
Mostly writing

@@

\begin{figure}[ht]
  \centering
  \caption[Comparison of original and modified normalised lineages-through-time]
    {Comparison of original formulation of normalized lineages-through-time,
     developed in~\autocite{janzen2015approximate}, with our modified version
     using linear interpolation. Here, the red and blue trees both have
     uniformly spaced branching times. Using step functions (left), the nLTT
     of the two trees is non-zero due to the differing numbers of internal
     branches. Using linear interpolation, the nLTT is zero (right). The lines
     on the right graph have been offset for visibility.}
  \includegraphics[scale=0.75]{nltt}
  \label{fig:nltt}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{separable}
  \caption[Separable versus non-separable pararameters in kernel space]{
    Separable versus non-separable parameters in kernel space. Trees have been
    simulated under three sets of parameters, represented as blue, red, and
    green. An observed tree is shown in black. Trees are layed out such that
    the distance between two trees corresponds to their similarity. In panel A,
    trees from the same parameter set are similar to each other, but different
    from other trees. The true tree is most consistent with the red parameters.
    In panels B and C, trees from the same parameter set are not similar to
    each other (B), or trees from different parameter sets are similar to each
    other (C). It's difficult to say which parameters the true tree is most
    consistent with.
  }
  \label{fig:separable}
\end{figure}

Before undertaking a complete ABC analysis, I analysed four simple contact
network models to determine whether their parameters could be separated in tree
kernel space. The four models are described in detail in
subsection~\ref{subsubsec:generative} of the introduction. Briefly, they are:
random networks, where each possible contact has a fixed probability of
occuring; preferential attachment networks, where highly connected nodes tend
to attract more contacts; small world networks, where nodes are connected to
their immediate neighbours and the occasional far-flung contact; and full
networks, where every possible connection is present. I will describe here only
the procedure and results for the preferential attachment networks. The details
of the other three types of graph can be found in the supplemental materials. A
graphical schematic of the analysis undertaken here is given in
Figure~\ref{fig:kernelexpt}.

\begin{figure}[ht]
  \centering
  \label{fig:kernelexpt}
  \includegraphics{kernel_expt}
  \caption[Schematic of first set of simulation experiments]{
    Schematic of first set of simulation experiments to determine separable
    parameters in kernel space, along with optimal tree kernel meta-parameters.
  }
\end{figure}

The method of testing for separability was described previously
in~\autocite{poon2015phylodynamic}, but I will reiterate it here for
completeness. As a concrete example, consider the attachment power parameter
\gls{alpha} of the preferential attachment networks. This parameter describes the
strength of attraction to highly connected nodes and is bounded below by zero
indicating no extra attraction. By qualitative observation, I determined that a
power of 2.0, which produced networks with very few ``hub'' nodes with
extremely high degree, was a suitable upper bound (see
Figure~\ref{fig:pabounds}). Therefore, I chose to test the values 0.5, 1.0, and
1.5 for separability. The other parameters were fixed: the number of nodes in
the network was 5000, and the mean degree of each node in the network was four.
As discussed in subsection~\ref{subsubsec:generative}, this is the smallest
mean degree value for preferential attachment networks which produces networks
which are more than trees.

\begin{figure}[ht]
  \centering
  \label{fig:pabounds}
  \includegraphics{pa_power_bounds}
  \caption[Upper and lower bounds on preferential attachment power]{
    Qualitative justification for choice of zero and two as lower and upper
    bounds on preferential attachment power $\alpha$. (A) Preferential
    attachment network on 50 nodes with $\alpha = 0$, the lower bound enforced
    by the model. (B) Preferential attachment network on 50 nodes with $\alpha
    = 2$, where a few nodes have very high degree but the majority have very
    low degree. (C) Density plot of node degrees in a 5000-node network with
    $\alpha = 0$. The maximum degree of a node in this network was 24. (D)
    Density plot of node degrees in a 5000-node network with $\alpha = 2$. The
    maximum degree of a node in this network was 4942. 
  }
\end{figure}

For each of the values of $\alpha$, I generated 100 networks on 5000 nodes. An
epidemic was simulated over each network (see subsection X) until 1000 nodes
were infected, and 500 of those infected nodes were sampled to form a
transmission tree. This resulted in 300 total simulated transmission trees -
100 for each of the three values of $\alpha$. The data generation steps are
shown on the left side of Figure~\ref{fig:kernelexpt}. Next, I computed the
tree kernel~\autocite{poon2013mapping} (see
subsection~\ref{subsubsec:treeshape}) for each pair of trees. These values were
placed into a 300 $\times$ 300 kernel matrix, where the value at the $(i, j)$th
position was the tree kernel of the $i$th and $j$th trees.

@@

\begin{figure}[ht]
  \centering
  \includegraphics{acc_prec}
  \caption{Illustration of accurate vs. precise kernel score estimates}
  \label{fig:accprec}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch_expt}
  \caption{Schematic of grid search simulation experiments.}
  \label{fig:gridsearch}
\end{figure}

@@

\subsection{Applications}

\subsubsection{HIV in British Columubia}

>>>>

\subsubsection*{Epidemic simulation}
\label{subsubsec:nettree}

@@

\begin{figure}[ht]
  \centering
  \caption[Comparison of original and modified normalised lineages-through-time]
    {Comparison of original formulation of normalized lineages-through-time,
     developed in~\autocite{janzen2015approximate}, with our modified version
     using linear interpolation. Here, the red and blue trees both have
     uniformly spaced branching times. Using step functions (left), the nLTT
     of the two trees is non-zero due to the differing numbers of internal
     branches. Using linear interpolation, the nLTT is zero (right). The lines
     on the right graph have been offset for visibility.}
  \includegraphics{nltt.pdf}
  \label{fig:nltt}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{separable.pdf}
  \caption[Separable versus non-separable pararameters in kernel space]{
    Separable versus non-separable parameters in kernel space. Trees have been
    simulated under three sets of parameters, represented as blue, red, and
    green. An observed tree is shown in black. Trees are layed out such that
    the distance between two trees corresponds to their similarity. In panel A,
    trees from the same parameter set are similar to each other, but different
    from other trees. The true tree is most consistent with the red parameters.
    In panels B and C, trees from the same parameter set are not similar to
    each other (B), or trees from different parameter sets are similar to each
    other (C). It's difficult to say which parameters the true tree is most
    consistent with.
  }
  \label{fig:separable}
\end{figure}

Before undertaking a complete ABC analysis, I analysed the parameters of the
\gls{BA} network model to to determine whether they could be separated in tree
kernel space. A graphical schematic of the analysis undertaken here is given in
Figure~\ref{fig:kernelexpt}.

\begin{figure}[ht]
  \centering
  \label{fig:kernelexpt}
  \includegraphics{kernel-expt.pdf}
  \caption[Schematic of first set of simulation experiments]{
    Schematic of first set of simulation experiments to determine separable
    parameters in kernel space, along with optimal tree kernel meta-parameters.
  }
\end{figure}

The method of testing for separability was described previously
in~\autocite{poon2015phylodynamic}. As a concrete example, consider the
attachment power parameter \gls{alpha}. This parameter describes the strength
of attraction to highly connected nodes and is bounded below by zero indicating
no extra attraction. By qualitative observation, I determined that a power of
2.0, which produced networks with very few ``hub'' nodes with extremely high
degree, was a suitable upper bound (see Figure~\ref{fig:alphabds}). Therefore,
I chose to test the values 0.5, 1.0, and 1.5 for separability. The other
parameters were fixed: the number of nodes in the network was 5000, and the
mean degree of each node in the network was four. As discussed in
subsection~\ref{subsubsec:generative}, this is the smallest mean degree value
for preferential attachment networks which produces networks which are more
than trees.

\begin{figure}[ht]
  \centering
  \label{fig:alphabds}
  \includegraphics{alpha-bounds.pdf}
  \caption[Upper and lower bounds on preferential attachment power]{
    Qualitative justification for choice of zero and two as lower and upper
    bounds on preferential attachment power $\alpha$. (A) Preferential
    attachment network on 50 nodes with $\alpha = 0$, the lower bound enforced
    by the model. (B) Preferential attachment network on 50 nodes with $\alpha
    = 2$, where a few nodes have very high degree but the majority have very
    low degree. (C) Density plot of node degrees in a 5000-node network with
    $\alpha = 0$. The maximum degree of a node in this network was 24. (D)
    Density plot of node degrees in a 5000-node network with $\alpha = 2$. The
    maximum degree of a node in this network was 4942. 
  }
\end{figure}

For each of the values of $\alpha$, I generated 100 networks, each with 5000
nodes. An epidemic was simulated over each network (see
\cref{subsubsec:nettree}) until 1000 nodes were infected, and 500 of those
infected nodes were sampled to form a transmission tree. This resulted in 300
total simulated transmission trees - 100 for each of the three values of
$\alpha$. The data generation steps are shown on the left side of
Figure~\ref{fig:kernelexpt}. Next, I computed the tree
kernel~\autocite{poon2013mapping} (see subsection~\ref{subsubsec:treeshape})
for each pair of trees. These values were placed into a 300 $\times$ 300 kernel
matrix, where the value at the $(i, j)$th position was the tree kernel of the
$i$th and $j$th trees.

@@

\begin{figure}[ht]
  \centering
  \includegraphics{acc-prec.pdf}
  \caption{Illustration of accurate vs. precise kernel score estimates}
  \label{fig:accprec}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch-expt.pdf}
  \caption{Schematic of grid search simulation experiments.}
  \label{fig:gridsearch}
\end{figure}

@@

\subsubsection{Characterization of power-law exponent in Barab\'asi-Albert networks}

Most studies of social network or transmission network
parameters~\autocite[e.g.][]{liljeros2001web, jones2003assessment,
schneeberger2004scale, brown2011transmission} report the coefficient
\gls{gamma} of the power law degree distribution. To make our results
comparable to previous work, we used simulated networks to investigate the
relationship between the \gls{BA} model parameters and \gls{gamma}. A network
was simulated for each element of the Cartesian product of these parameters:
\gls{N} = \sett{500, 600, \ldots, 15000}, \gls{m} = \sett{1, 2, \ldots, 8}, and
\gls{alpha} = \sett{0.00, 0.01, \ldots, 2.00}. A power law distribution was
fitted to the degree distribution of each simulated network using the
\software{fit\_power\_law} function in \software{igraph} with the `R.mle'
implementation. We fitted a \gls{GLM} with Gamma-distributed errors and a log
link function to the observed distribution of \gls{gamma} values, with
\gls{alpha}, \gls{m}, \gls{N}, and all possible interaction terms as
predictors.

\subsection{Real data experiments}

We applied kernel-ABC to six published HIV datasets, summarized in
\cref{tab:realdata}.

\begin{table}
  \centering
  \input{\tablepath/realdata-bc}
  \caption{Characteristics of published HIV datasets analysed with kernel-ABC.}
  \label{tab:realdata}
\end{table}

### 2016-03-17 doc/thesis/objective.tex
Mostly writing

A second, more recent group of studies has evaluated the effect of network
structure on transmission tree shape. The use of models which assume a
\defn{panmictic} (that is, homogeneously mixed) population in phylodynamics has
become widespread, so it is natural that some researchers have investigated the
effects of this assumption. In particular, since phylodynamic methods use
phylogenies as their data source, several studies have examined the shapes of
phylogenies arising from non-panmictic populations. 
\citeauthor{o2010contact}~(\citeyear{o2010contact}) simulated epidemics over
networks with four types of degree distribution. They then estimated the
Bayesian skyride~\autocite{minin2008smooth} population size trajectory in two
ways: from the phylogeny, using \gls{MCMC}; and from the incidence and
prevalence trajectories, using the method developed by Volz
\etal~\autocite{volz2009phylodynamics}. They found that the concordance between
the two skyrides, as well as the relationship between the skyride and
prevalence curve, was qualitatively different for each degree distribution.
\citeauthor{leventhal2012inferring} simulated transmission trees over \gls{ER},
\gls{WS}, \gls{BA}, and full networks with fixed number of nodes and mean
degree. They calculated Sackin's index of the simulated trees while varying the
epidemic, network, and sampling parameters, and found that the relationship
between these parameters and Sackin's index varies considerably among the
different network models. In summary, studies in this group have demonstrated
that network structure profoundly influences tree shape, but have not attempted
to quantitatively infer network parameters from observed trees.

Finally, a third group of studies has used Bayesian methods to infer a
structural network parameter from observed infection and recovery times. This
third group is most similar in aims to our own work; rather than using
epidemiological observations, we employ viral phylogenies. The pioneering study
in this group was by
\citeauthor{britton2002bayesian}~(\citeyear{britton2002bayesian}), who
developed a Bayesian method to infer the $p$ parameter of an \gls{ER} network,
along with the $\beta$ and $\gamma$ parameters of \gls{SI} model. Their method
is able to use either infection and removal times, or removal times only.
However, it is designed for only a small number of observations (15 and 42
cases in their applications), and their estimates of $p$ for real outbreaks
were mostly uninformative (95\% confidence intervals [0.11-0.96] and
0.055-0.96]; $p$ is bounded in [0, 1]).
\citeauthor{groendyke2011bayesian}~(\citeyear{groendyke2011bayesian})
significantly updated and extended the methodology of
\citeauthor{britton2002bayesian}, and applied it to a measles outbreak
affecting 188 individuals. They were able to obtain a much more informative
estimate of $p$, although this data set included both symptom onset and
recovery times for all individuals. They also assumed that the entire network
was infected, so that the network size was exactly 188. It is unclear how well
their method would scale to networks with thousands of nodes.

>>>>

The use of models which assume a \defn{panmictic} (that is, homogeneously
mixed) population in phylodynamics has become widespread, so it is natural that
some researchers have investigated the effects of this assumption. In
particular, since phylodynamic methods use phylogenies as their data source,
several studies have examined the shapes of phylogenies arising from
non-panmictic populations.

Finally, a third group of studies has used Bayesian methods to infer a
structural network parameter from observed infection and recovery times. This
third group is most similar in aims to our own work; rather than using
epidemiological observations, we employ viral phylogenies. These were discussed
in \cref{subsec:netoverview}.

### 2016-03-17 doc/thesis/results.Rnw
Mostly writing

\begin{figure}[ht]
  \centering
  \label{fig:patrees}
  \includegraphics{kernel_pa_trees}
  \caption[Visibly distinctive trees simulated under three values of \gls{alpha}]{
    Epidemics of 1000 infected were simulated on \gls{BA} networks of 5000
    nodes, with \gls{alpha} equal to 0.5, 1.0, or 1.5. Transmission trees were
    created by sampling 500 infected nodes. Higher \gls{alpha} values produce
    networks with a small number of highly-connected nodes, which results in a
    highly unbalanced, ladder-like tree structure.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \label{fig:pacrossv}
  \includegraphics{kernel_pa_crossv}
  \caption[Cross-validation performance of kernel support vector machine
  classifier for preferential attachment power]{
    Cross-validation performance of kernel support vector machine classifier
    for preferential attachment power.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \label{fig:pakpca}
  \includegraphics{kernel_pa_kpca}
  \caption[Projection of kernel matrix for different attachment power values
  onto its first two principal components]{
    Projection of the kernel matrix for different preferential attachment power
    values onto its first two principal components, for eight simulation
    scenarios. Each point corresponds to a simulated transmission tree, and is
    coloured by preferential attachment power. Facets are number of infected
    nodes (horizontal), and number of sampled tips (vertical). The parameters
    to the tree kernel were $\lambda = 0.3$ and $\sigma = 4$, and the nLTT was
    not used. Qualitatively, trees with a larger number of tips are easier to
    separate in kernel space, regardless of what sampling proportion they
    represent. In all cases, the highest attachment power can be separated from
    the other two, but the two lowest values become hand to distinguish with in
    the 100-tip trees.
  }
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \label{fig:prevtrees}
  \includegraphics{kernel_nsimnode_trees}
  \caption[Similarly shaped simulated under three values of \gls{I}]{
    Epidemics were simulated on networks of size 5000 until \gls{I} = 500,
    1000, or 2000 nodes were infected. When scaled to the same height, there is
    no immediately visible distinction in shape between trees simulated under
    different \gls{I} values.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \label{fig:prevcrossv}
  \includegraphics{kernel_nsimnode_crossv}
  \caption[Cross-validation performance of kernel-\gls{SVM} classifier for
           prevalence]{
    For \gls{BA} networks of size \gls{N} = 5000, a kernel-\gls{SVM} classifier
    is very accurate at predicting \gls{I}. Epidemics were simulated until
    \gls{I} = 500, 1000, or 2000 nodes were infected, and either 100 or 500
    nodes were sampled for inclusion in a transmission tree. The parameters of
    the \gls{BA} network were \gls{alpha} = 1.0 and \gls{m} = 2. A Sackin's
    index-based classifier performed very poorly on these data ($R^2 = $ TODO
    for 100-tip trees and blah for 500-tip trees, not shown).
  }
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch_pa_kernel}
  \caption[Grid search kernel scores]{
    Grid search kernel scores for testing trees simulated under various
    \gls{alpha} values. All epidemics had \gls{I} = 1000 infected nodes, on
    \gls{BA} networks of size \gls{N} = 5000 with \gls{m} fixed at 2. Colours
    indicate the number of sampled tips.
  }
  \label{fig:gridkernel}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch_pa_estimates}
  \caption[Marginal estimates of \gls{alpha} obtained with grid search]{
    Marginal estimates of \gls{alpha} obtained with grid search. Training trees
    were simulated on a narrowly spaced grid of \gls{alpha} values, and
    compared to testing trees using the tree kernel. The \gls{alpha} value in
    the grid with the highest median kernel score was taken as the point
    estimate for the testing tree. These point estimates are shown as black
    dots. The dashed line is the identity.
  }
  \label{fig:gridest}
\end{figure}

@@

We used kernel-\gls{ABC} to estimate the parameters of the \gls{BA} model 
on simulated trees where the true parameter values were known. Point estimates
for each parameter are shown in Figure~\ref{fig:abcpt}. Of the four parameters,
$\alpha$ was the most accurately estimated, with a median [IQR] absolute error
of 
    \Sexpr{d[,median(alpha_error)]} 
    [\Sexpr{d[,quantile(alpha_error, 0.25)]}-\Sexpr{d[,quantile(alpha_error, 0.75)]}].
The accuracy of the estimates was not significantly different between values of
$m$ or $I$ (both one-way ANOVA,
    $p$ = \Sexpr{alpha.av["factor(true_m)", "Pr(>F)"]}
and 
    \Sexpr{alpha.av["factor(true_I)", "Pr(>F)"]}),
although the errors when the true value of $\alpha$ was zero were
significantly greater than the other values 
    (Wilcoxon rank-sum test, $p$ = \Sexpr{zero.alpha.test$p.value}).
The error in the estimated value of $I$ was
    \Sexpr{d[,median(I_error)]} 
    [\Sexpr{d[,quantile(I_error, 0.25)]}-\Sexpr{d[,quantile(I_error, 0.75)]}].
Errors were significantly higher for $\alpha \geq 1$
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.I.test$p.value})
and for $I$ = 2000
    ($p$ = \Sexpr{I.I.test$p.value}),
but not for any values of $m$
    (one-way ANOVA, $p$ = \Sexpr{I.av["factor(true_m)", "Pr(>F)"]}).
The $m$ parameter was estimated correctly in
    \Sexpr{as.integer(m.tbl[1] * 100)} \%
of simulations, with an error of one in
    \Sexpr{as.integer(m.tbl[2] * 100)} \%
and of two or more in 
    \Sexpr{as.integer(sum(m.tbl[3:length(m.tbl)]) * 100)} \%
(the only possible $m$ values were 2, 3, 4, or 5). The true values of
$m$ and $I$ did not significantly affect the error
    (one-way ANOVA, $p$ = \Sexpr{m.av["factor(true_m)", "Pr(>F)"]} and
                          \Sexpr{m.av["factor(true_I)", "Pr(>F)"]}),
but the accuracy was significantly lower for integral than non-integral
values of $\alpha$
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.m.test$p.value}).
Finally, the total number of nodes $N$ was consistently over-estimated by about
a factor of two
    (error \Sexpr{d[,median(N_error)]} 
    [\Sexpr{d[,quantile(N_error, 0.25)]}-\Sexpr{d[,quantile(N_error, 0.75)]}]).
No other parameters influenced the accuracy of the $N$ estimates 
    (one-way ANOVA, $p \geq$ \Sexpr{min(N.av[,"Pr(>F)"])}).

Figure~\ref{fig:abcex} shows the \gls{ABC} approximation to the
posterior distribution on the \gls{BA} parameters for one simulation
(equivalent plots for all the simulations can be found in the supplemental
materials). \gls{HPD} intervals around $\alpha$ and $I$ were narrow relative
to the region of nonzero prior density, whereas the intervals for $m$ and $N$
were widely dispersed. Table~\ref{tab:abchpd} shows point estimates and 95\%
\gls{HPD} intervals averaged over all simulations.

>>>>

\begin{figure}[ht]
  \centering
  \label{fig:patrees}
  \includegraphics{kernel-alpha-tree.pdf}
  \caption[Visibly distinctive trees simulated under three values of \gls{alpha}]{
    Epidemics of 1000 infected were simulated on \gls{BA} networks of 5000
    nodes, with \gls{alpha} equal to 0.5, 1.0, or 1.5. Transmission trees were
    created by sampling 500 infected nodes. Higher \gls{alpha} values produce
    networks with a small number of highly-connected nodes, which results in a
    highly unbalanced, ladder-like tree structure.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \label{fig:pacrossv}
  \includegraphics{kernel-alpha-crossv.pdf}
  \caption[Cross-validation performance of kernel support vector machine
  classifier for preferential attachment power]{
    Cross-validation performance of kernel support vector machine classifier
    for preferential attachment power.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \label{fig:pakpca}
  \includegraphics{kernel-kpca.pdf}
  \caption[Projection of kernel matrix for different attachment power values
  onto its first two principal components]{
    Projection of the kernel matrix for different preferential attachment power
    values onto its first two principal components, for eight simulation
    scenarios. Each point corresponds to a simulated transmission tree, and is
    coloured by preferential attachment power. Facets are number of infected
    nodes (horizontal), and number of sampled tips (vertical). The parameters
    to the tree kernel were $\lambda = 0.3$ and $\sigma = 4$, and the nLTT was
    not used. Qualitatively, trees with a larger number of tips are easier to
    separate in kernel space, regardless of what sampling proportion they
    represent. In all cases, the highest attachment power can be separated from
    the other two, but the two lowest values become hand to distinguish with in
    the 100-tip trees.
  }
\end{figure}

@@

@@

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch-alpha-kernel.pdf}
  \caption[Grid search kernel scores]{
    Grid search kernel scores for testing trees simulated under various
    \gls{alpha} values. All epidemics had \gls{I} = 1000 infected nodes, on
    \gls{BA} networks of size \gls{N} = 5000 with \gls{m} fixed at 2. Colours
    indicate the number of sampled tips.
  }
  \label{fig:gridkernel}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics{gridsearch-alpha-point-estimate.pdf}
  \caption[Marginal estimates of \gls{alpha} obtained with grid search]{
    Marginal estimates of \gls{alpha} obtained with grid search. Training trees
    were simulated on a narrowly spaced grid of \gls{alpha} values, and
    compared to testing trees using the tree kernel. The \gls{alpha} value in
    the grid with the highest median kernel score was taken as the point
    estimate for the testing tree. These point estimates are shown as black
    dots. The dashed line is the identity.
  }
  \label{fig:gridest}
\end{figure}

@@

We used kernel-\gls{ABC} to estimate the parameters of the \gls{BA} model 
on simulated trees where the true parameter values were known. Point estimates
for each parameter are shown in Figure~\ref{fig:abcpt}. Of the four parameters,
\gls{alpha} was the most accurately estimated, with a median [IQR] absolute error
of 
    \Sexpr{d[,median(alpha_error)]} 
    [\Sexpr{d[,quantile(alpha_error, 0.25)]}-\Sexpr{d[,quantile(alpha_error, 0.75)]}].
The accuracy of the estimates was not significantly different between values of
$m$ or $I$ (both one-way ANOVA,
    $p$ = \Sexpr{alpha.av["factor(true_m)", "Pr(>F)"]}
and 
    \Sexpr{alpha.av["factor(true_I)", "Pr(>F)"]}),
although the errors when the true value of \gls{alpha} was zero were
significantly greater than the other values 
    (Wilcoxon rank-sum test, $p$ = \Sexpr{zero.alpha.test$p.value}).
The error in the estimated value of $I$ was
    \Sexpr{d[,median(I_error)]} 
    [\Sexpr{d[,quantile(I_error, 0.25)]}-\Sexpr{d[,quantile(I_error, 0.75)]}].
Errors were significantly higher for $\alpha \geq 1$
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.I.test$p.value})
and for $I$ = 2000
    ($p$ = \Sexpr{I.I.test$p.value}),
but not for any values of $m$
    (one-way ANOVA, $p$ = \Sexpr{I.av["factor(true_m)", "Pr(>F)"]}).
The $m$ parameter was estimated correctly in
    \Sexpr{as.integer(m.tbl[1] * 100)} \%
of simulations, with an error of one in
    \Sexpr{as.integer(m.tbl[2] * 100)} \%
and of two or more in 
    \Sexpr{as.integer(sum(m.tbl[3:length(m.tbl)]) * 100)} \%
(the only possible $m$ values were 2, 3, 4, or 5). The true values of
$m$ and $I$ did not significantly affect the error
    (one-way ANOVA, $p$ = \Sexpr{m.av["factor(true_m)", "Pr(>F)"]} and
                          \Sexpr{m.av["factor(true_I)", "Pr(>F)"]}),
but the accuracy was significantly lower for integral than non-integral
values of \gls{alpha}
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.m.test$p.value}).
Finally, the total number of nodes \gls{N} was consistently over-estimated by
about a factor of two
    (error \Sexpr{d[,median(N_error)]} 
    [\Sexpr{d[,quantile(N_error, 0.25)]}-\Sexpr{d[,quantile(N_error, 0.75)]}]).
No other parameters influenced the accuracy of the $N$ estimates 
    (one-way ANOVA, $p \geq$ \Sexpr{min(N.av[,"Pr(>F)"])}).

Figure~\ref{fig:abcex} shows the \gls{ABC} approximation to the
posterior distribution on the \gls{BA} parameters for one simulation
(equivalent plots for all the simulations can be found in the supplemental
materials). \Gls{HPD} intervals around \gls{alpha} and \gls{I} were narrow
relative to the region of nonzero prior density, whereas the intervals for $m$
and \gls{N} were widely dispersed. Table~\ref{tab:abchpd} shows point estimates and
95\% \gls{HPD} intervals averaged over all simulations.

\begin{table}
    \centering
    \input{\tablepath/abc-hpd}
    \caption{Average widths of 95\% confidence intervals for \gls{BA} model
    parameters estimated with kernel-\gls{ABC}.}
    \label{tab:glm}
\end{table}

\subsection{Characterization of power-law exponent in Barab\'asi-Albert networks}

\Cref{tab:glm} shows the estimated parameters for a log-link \gls{GLM} fitted
to the observed distribution of \gls{gamma} values. The coefficients are
interpretable as multiplicative effects.

\begin{table}
    \centering
    \input{\tablepath/pa-gamma-glm}
    \caption{Estimated \gls{GLM} parameters for relationship between power-law
    exponent \gls{gamma} and \gls{BA} model parameters.}
    \label{tab:glm}
\end{table}
